\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/experiments.tex
Explain why we can't pre-train models

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar.png}
\caption{Query runtimes with imputation on base tables, \ProjectName{}
    optimizing for quality ($\alpha=0$), and \ProjectName{} optimizing for
    performance ($\alpha=1$). Quality-optimized, on-the-fly imputation provides an order of
    magnitude speedup over imputing on base tables. Efficiency-optimized on-the-fly
    imputation can provide another order-of-magnitude speedup at the expense of quality. For
    relatively expensive queries over large datasets (Query 9), runtime of imputation can be reduced from \acsbaseresulthours~to \acsimputedbzeroresult.}

@@

\subsubsection{Runtime of Base-table Imputation}
In many real-world cases, applying the imputation step at the base table is prohibitively
expensive.
To illustrate the increasing difficulty of such an approach as datasets scale, we run~\Cref{q9} over the ACS dataset.
Applying the imputation operation to the base table is extremely expensive, in our case
completing in \acsbaseresultminutes (\Cref{fig:runtimes}. In contrast, \ProjectName{} executes a quality-optimized version
in\acsimputedbzeroresult~and a runtime-optimized version in \acsimputedboneresult. This highlights the potential
benefit of using our system for early data exploration.

\srm{note somewhere that imputation requires both training and running model, and state why this is reasonable / the only choice}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar.png}
\caption{Query runtimes with imputation on base tables, \ProjectName{}
    optimizing for quality ($\alpha=0$), and \ProjectName{} optimizing for
    performance ($\alpha=1$). Quality-optimized, on-the-fly imputation provides an order of
    magnitude speedup over imputing on base tables. Efficiency-optimized on-the-fly
    imputation can provide another order-of-magnitude speedup at the expense of quality. For
    relatively expensive queries over large datasets (Query 9), runtime of imputation can be reduced
    from~\acsbaseresulthours~to~\acsimputedbzeroresult.}

@@

\subsubsection{Runtime of Base-table Imputation}
In many real-world cases, applying the imputation step at the base table is prohibitively
expensive.
To illustrate the increasing difficulty of such an approach as datasets scale, we run~\Cref{q9} over the ACS dataset.
Applying the imputation operation to the base table is extremely expensive, in our case
completing in \acsbaseresultminutes~(\Cref{fig:runtimes}). In contrast, \ProjectName{} executes a quality-optimized version
in~\acsimputedbzeroresult~and a runtime-optimized version in~\acsimputedboneresult. This highlights the potential
benefit of using our system for early data exploration.

For every imputation inserted into the query plan, a new statistical model is instantiated and trained before being used for imputation.
Although it is tempting to further optimize query execution in \ProjectName{} by pre-training imputation models while the analyst begins to make queries,
this is not desirable because the specific rows of data, set of complete attributes, and set of attributes to impute are not known until runtime.
Furthermore, at that point, it may make more sense to specify a coherent model over the entire base table instead.
